Supporting Dynamic Data Partitioning in Distributed Memory Architectures with Logical Regions

### 2012-11-03 doc/types-pldi2013/langdef.tex
bunch of little edits - pushed over 10 pages, but fixable

Figure~\ref{fig:langdef} defines Core Legion, a subset of the full Legion language
that still illustrates all of the important issues.  
%Types include booleans, integers, tuples, and pointers.  
Pointers are annotated with a list of regions---a non-null pointer must point to a 
location that is contained in at least one of the regions. There is a special
{\em coloring} type, used to specify partitions of regions into subregions.
%Functions in Legion are named, accept one or more arguments and
%return a value of some type.  
Functions declare the region
access privileges and coherence they require.  Some function instances are {\em tasks}; a function may be executed
within the current task or run in parallel as a separate (sub)task---this decision is made
by the Legion task scheduler.  Function types are
universally quantified over all region names appearing in the type.
The other important type is a {\em region relationship}, an instance of which captures a value and
one or more regions satisfying associated constraints.  A region relation instance
can be written into the heap and later read and
unpacked, giving new local names to the regions contained in
the instance.

@@

A representative selection of the type rules is given in Figure~\ref{fig:langrules}.  Both $\Phi$ and $\Omega$ are used in the heap access expressions {\em read}, {\em write}, and {\em reduce}.
A valid heap access has the needed permission for logical region(s) in the
pointer's type.  Note the exact region need not be named in $\Phi$ if permissions
exist for a logical region that provably contains the pointer's region.  To simplify this check, Figure~\ref{fig:closure}
defines closure operations $\Omega^*$ (all constraints implied by $\Omega$) and
$\Phi^*$ (all privileges implied by $\Phi$ and $\Omega^*$).

@@

Region constraints are introduced by the {\em partition} expression,
which makes use of {\em colorings}, a new type specific to Legion.  A coloring is an opaque mapping from
pointers (which must point into the region being colored) to integer {\em color} values.  
%(For simplicity, 
%Core Legion allows only an iterative construction of a coloring via a {\em newcolor} expression that generates
%an empty map, and a {\em color} expression which adds a new entry to an existing map. The opacity of the
%coloring allows for more efficient generation (and storage) of colorings as needed.)  
Partitioning introduces names for subregions corresponding to each color in the coloring, guaranteeing that each
subregion is disjoint from the others and all are subregions of the original region.

The {\em pack} and {\em unpack} expressions allow regions to be stored in the heap.
%  Logical region names are lexically scoped and if stored in the heap as-is, can only be read within the same scope.  
A {\em region relationship} captures statically known constraints between regions;
because the {\em pack} rule verifies these constraints hold when the 
region relationship value is created,{\em unpack} can reintroduce these constraints on
the (fresh) logical region names when the value is read and unpacked from the heap.
Crucially for soundness,  region relationships do not capture privileges.
%
% FIXME  It would be nice to add some comments about unpack here, and how the constraints introduced by unpack
% must be sufficient to allow access to the new regions if they are to be used, which generally requires the type
% have a free region variable capturing subregioning relationships between the packed regions and some existing region
% in scope for which privileges are held.
% 
Finally, task calls verify the requirement that the privileges held by a called task are a subset of those held
by the caller.  In addition to being necessary for the proof of soundness, this property is critical to
enabling hierarchical and distributed scheduling of tasks.

@@

We show the most interesting operational rules for Core Legion in
Figure~\ref{fig:langrules}.  The rules for the {\em read}, {\em
write}, and {\em reduce} show how dynamic memory traces are
constructed and how the result of a read expression is relaxed when
the location falls within the clobber set.  Additionally, the write
and reduce operations, with their two subexpressions, demonstrate how
the traces of subexpressions are interleaved within the environment
(and clobber set) of the parent expression.  (A formal definition of
the {\em valid\_interleave} predicate can be found in
Figure~\ref{fig:validinterleave}, and will be discussed in
Section~\ref{sec:coherence}.)

@@

Our first results shows a well-typed expression accesses the heap in ways consistent with its static privileges.
A judgment $\privconsist{E}{\Phi}$ holds if memory operations in memory trace $E$ have types and
locations covered by privileges $\Phi$:
\[ 
\begin{array}{l}
\privconsist{E}{\Phi} \Leftrightarrow \forall \epsilon \in E. \\
\quad\quad (\epsilon = read(l, c, v) \Rightarrow \exists r. l \in M(r) \wedge reads(r) \in \Phi)\ \wedge \\
\quad\quad (\epsilon = write(l, c, v) \Rightarrow \exists r. l \in M(r) \wedge writes(r) \in \Phi)\ \wedge \\
\quad\quad (\epsilon = reduce_{id}(l, c, v) \Rightarrow \exists r. l \in M(r) \wedge reduces_{id}(r) \in \Phi)
\end{array}
\]

@@

An important insight from the proof of Theorem~\ref{thm:effects} is that 
it does not rely on the definition of {\em valid\_interleave}.  Weakening 
{\em valid\_interleave} to {\em any\_interleave} (Figure~\ref{fig:validinterleave}), 
which  allows arbitrary interleavings of memory traces from subexpressions, 
is sufficient for the proof of soundness.  
The stronger constraints in {\em valid\_interleave}
(Figure~\ref{fig:validinterleave}) address the coherence of heap accesses;
{\em valid\_interleave} specifies permitted interleavings of memory operations for
the particular coherence modes on logical regions.

@@

To determine when parallel execution is safe, we start from the sequential execution trace and allow the reordering of 
adjacent heap operations that do not change the behavior of the application.  If we can show that it is safe to 
reorder any pair of operations that come from two different constituent traces, then any interleaving of the constituent
traces will be equivalent to a sequential execution and parallel execution is safe.  To
efficiently discover these cases at runtime, we require a test that can determine this property prior
to the actual execution of the tasks that create the traces.  We show that a test based on the subtask privileges and 
the current region mapping can soundly predict when this property will hold.
%If we can show that reordering is allowed
%between any two operations that come from different constituent traces, any interleaving of the constituent traces will
%be equivalent to the serialized execution and parallel execution was safe.  Finally, to allow the safety of parallel
%execution to be determined {\em before} the execution is actually performed, we show that a test based on the subtask
%privileges and the current region mapping can soundly predict when this property will hold.
We define a {\em non-interference} operator $\epsilon_1 \nonint \epsilon_2$ on two memory operations:
$$
\begin{array}{l@{ }l}
op_1(l_1, c_1,& v_1)\ \nonint\ op_2(l_2, c_2, v_2) \Leftrightarrow l_1 \not= l_2 \vee \\
& (op_1 = read \wedge op_2 = read)\ \vee \\
& (op_1 = reduce_{id_1} \wedge op_2 = reduce_{id_2} \wedge id_1 = id_2)
\end{array}
$$
Accesses to different locations cannot affect each other, and reads have no side-effects.  The safety of the third case
follows from the requirement that reduction operations be commutative.  
We next show that this non-interference operator preserves the validity of an interleaving
of two or more traces when reordering a pair of memory operations.
\begin{lem}
\label{lem:nonintswap}
\rm
Let $S$ be a store, $C$ a clobber set, $\oton{E}, E'_a, E'_b$ memory traces, and
$\epsilon_1, \epsilon_2$ be two memory operations from $E_i$ and $E_j$ ($i \not= j$).  Then,
$$\begin{array}{l@{}l}
valid\_interleave&(S, C, E'_a \dplus [ \epsilon_1, \epsilon_2 ] \dplus E'_b, \oton{E}) \wedge \epsilon_1 \nonint \epsilon_2 \Rightarrow \\
 & valid\_interleave(S, C, E'_a \dplus [ \epsilon_2, \epsilon_1 ] \dplus E'_b, \oton{E}).
\end{array}$$
\end{lem}
%The proof follows from the definitions of {\em coherent} and {\em seq\_equiv} in Figure~\ref{fig:validinterleave}.

@@

We highlight an important aspect of a Legion
implementation that is different from other systems and relies on the
soundness of privileges.  Dynamic non-interference of 
memory operations can only be determined after 
evaluation of an expression is completed, and only at great expense, 
as illustrated by work on transactional
memory \cite{Harris05}.  
%However, many systems are willing to pay this cost to
%extract parallelism from operations that access aliased data. 
At the other extreme are systems like 
Jade \cite{Rinard98} and DPJ \cite{Bocchino11} that check non-interference 
statically by disallowing aliasing.  In contrast, Legion checks non-interference of privileges
at runtime, which is much simpler and more efficient than checking
non-interference of dynamic memory traces.  Even though the privileges
themselves are static, the region mapping $M$ is dynamic.  Dynamically testing non-interference 
on the privileges of physical regions allows parallel execution in many more cases than a purely 
static analysis can achieve in the presence of aliasing.

@@

In cases where Legion cannot safely infer non-interference of
privileges (perhaps because two tasks actually access the same data in aliased regions) 
parallel execution can
still be requested by the programmer through the use of relaxed coherence 
annotations on individual regions passed to a task.
%the default behavior of sequential execution can
%be avoided through the use of relaxed coherence.
The {\em atomic} coherence mode specifies that although two
tasks interfere due to accessing aliased regions, they may execute in either order, allowing
the task issued later in program order to possibly run before the task issued earlier 
in program order.  This relaxation only applies if all aliased regions are annotated with atomic coherence.
%or a more relaxed coherence mode (see Section~\ref{subsec:coherencesimult}).
To show this is safe, we define a relaxed version of non-interference for atomic coherence:
$$
\begin{array}{l@{}l}
op_1(l_1, c_1, v_1)\ \nonint^A\ op_2(l_2, c_2, v_2) \Leftrightarrow &op_1(l_1, c_1, v_1)\ \nonint\ op_2(l_2, c_2, v_2) \vee \\
& (c_1 = atomic \wedge c_2 = atomic)
\end{array}$$

@@

\texcomment{
Let $e_1$ and $e_2$ be well-typed Legion expressions using privileges $\Phi_1$ and
$\Phi_2$.  Now let $e_3$ be some subexpression of $e_1$ and $e_4$ be some 
subexpression of $e_2$, with corresponding privileges $\Phi_3$ and $\Phi_4$.
By Theorem~\ref{thm:parallelexec}, if the runtime can verify $\Phi_1 \nonint[M] \Phi_2$, then 
expressions $e_1$ and $e_2$ may be evaluated in parallel.  The evaluation of the subexpressions
$e_3$ and $e_4$ will therefore be allowed to run in parallel, and we must show that this is
permissible.  We do so by proving that any memory traces that can result from the evaluation
of the subexpression must be non-interfering (allowing parallel execution by
Lemma~\ref{lem:noninteffects}).
}
\begin{thm}
\label{thm:hiersched}
\rm
Let $e_1$ and $e_2$ be well-typed expressions using privileges $\Phi_1$ and
$\Phi_2$ respectively, where $\Phi_1 \nonint[M] \Phi_2$.  Let $e_3$ be a subexpression of $e_1$ and $e_4$ be a 
subexpression of $e_2$.  Any memory traces $E_3$ of $e_3$ and $E_4$ of $e_4$ resulting from evaluation of
$e_1$ and $e_2$ (with the usual consistent $M$, $L$, $H$, and $S$) are 
non-interfering.
\end{thm}
\texcomment{
\begin{proof}
Let $E_1$ be the result of an evaluation of $e_1$, with $E_3$ being the memory trace from the
evaluation of $e_3$ within the expression tree.  $E_1$ will be formed from a tree of valid
interleavings, each of which must include all the memory operations of each constituent trace.
By induction over the number of intermediate subexpressions between $e_1$ and $e_3$, we
can show that any memory operation $\epsilon_3$ that is in $E_3$ must also be in $E_1$.
Similarly, any memory operation $\epsilon_4$ that is in $E_4$ must also be in $E_2$.  We have
$E_1 \nonint E_2$ from Lemma~\ref{lem:nonintpriv}, so and therefore $\epsilon_3 \nonint \epsilon_4$.  Since
this holds for all $\epsilon_3$ in $E_3$ and all $\epsilon_4$ in $E_4$, we have $E_3 \nonint E_4$.
\end{proof}
} The Legion task scheduler uses Theorem~\ref{thm:hiersched} as follows: 
sibling function calls (those invoked within the same
function body) $e_1$ and $e_2$ are checked for non-interference of their (dynamic)
privileges.  Since $e_1$ and $e_2$ are guaranteed to be created on the node on which their parent
is running, no communication is required to perform the non-interference
test.  If they interfere they are executed in program order or serialized
depending on their coherence specifications; otherwise they are
considered for execution as parallel subtasks.    If $e_1$ and $e_2$ are 
determined to be non-interfering and are scheduled in parallel on different 
remote processors then Theorem~\ref{thm:hiersched}
guarantees that there is no communication required between $e_1$ and $e_2$
to perform non-interference tests between their sub-tasks.  Therefore,
the runtime requires no communication for scheduling.

>>>>

Figure~\ref{fig:langdef} defines Core Legion, a subset of the full Legion language
that still illustrates all of the important issues.  
%Types include booleans, integers, tuples, and pointers.  
Pointers are annotated with a list of logical regions---a non-null pointer must point to a 
location that is contained in at least one of the regions. There is a special
{\em coloring} type, used to specify partitions of regions into subregions.
%Functions in Legion are named, accept one or more arguments and
%return a value of some type.  
Functions declare the region
access privileges and coherence they require.  Some function instances are {\em tasks}; a function may be executed
within the current task or run in parallel as a separate (sub)task---this decision is made
by the Legion task scheduler.  Function types are
universally quantified over all region names appearing in the type.
The other important type is a {\em region relationship}, an instance of which captures a value and
one or more regions satisfying associated constraints.  A region relation instance
can be written into the heap and later read and
unpacked, giving new local names to the regions contained in
the instance.

@@

A representative selection of the type rules is given in Figure~\ref{fig:langrules}.  Both $\Phi$ and $\Omega$ are used in the heap access expressions {\em read}, {\em write}, and {\em reduce}.
A valid heap access has the needed permission for logical region(s) in the
pointer's type.  Note the exact region need not be named in $\Phi$ if permissions
exist for logical regions that provably contain the pointer's region(s).  To simplify this check, Figure~\ref{fig:closure}
defines closure operations $\Omega^*$ (all constraints implied by $\Omega$) and
$\Phi^*$ (all privileges implied by $\Phi$ and $\Omega^*$).

@@

Region constraints are introduced by the {\em partition} expression,
which makes use of {\em colorings}, a new type specific to Legion.  A coloring is an opaque mapping from
pointers (which must point into the region being colored) to integer {\em color} values.  
%(For simplicity, 
%Core Legion allows only an iterative construction of a coloring via a {\em newcolor} expression that generates
%an empty map, and a {\em color} expression which adds a new entry to an existing map. The opacity of the
%coloring allows for more efficient generation (and storage) of colorings as needed.)  
Partitioning introduces names for the subregions corresponding to each color in the coloring, guaranteeing that each
subregion is disjoint from the others and all are subregions of the original region.

The {\em pack} and {\em unpack} expressions allow regions and pointers into those regions to be stored in the heap.
%  Logical region names are lexically scoped and if stored in the heap as-is, can only be read within the same scope.  
A {\em region relationship} captures statically known constraints between regions;
because the {\em pack} rule verifies these constraints hold when the 
region relationship value is created,{\em unpack} can reintroduce these constraints on
the (fresh) logical region names when the value is read and unpacked from the heap.
Crucially for soundness,  region relationships do not capture privileges.
%
% FIXME  It would be nice to add some comments about unpack here, and how the constraints introduced by unpack
% must be sufficient to allow access to the new regions if they are to be used, which generally requires the type
% have a free region variable capturing subregioning relationships between the packed regions and some existing region
% in scope for which privileges are held.
% 
Finally, task calls verify the requirement that the privileges held by a called task are a subset of those held
by the caller.  In addition to being necessary for the proof of soundness, this property is critical to
enabling hierarchical and distributed scheduling of tasks.

@@

We show the most interesting operational rules for Core Legion in
Figure~\ref{fig:langrules}.  The rules for the {\em read}, {\em
write}, and {\em reduce} show how dynamic memory traces are
constructed and how the result of a read expression is relaxed when
the location falls within the clobber set.  The write
and reduce operations, with their two subexpressions, also demonstrate how
the traces of subexpressions are interleaved within the environment
(and clobber set) of the parent expression.  (A formal definition of
the {\em valid\_interleave} predicate can be found in
Figure~\ref{fig:validinterleave}, and will be discussed in
Section~\ref{sec:coherence}.)

@@

Our first result shows a well-typed expression accesses the heap in ways consistent with its static privileges.
A judgment $\privconsist{E}{\Phi}$ holds if memory operations in memory trace $E$ have types and
locations covered by privileges $\Phi$:
\[ 
\begin{array}{l}
\privconsist{E}{\Phi} \Leftrightarrow \forall \epsilon \in E. \\
\quad\quad (\epsilon = read(l, c, v) \Rightarrow \exists r. l \in M(r) \wedge reads(r) \in \Phi)\ \wedge \\
\quad\quad (\epsilon = write(l, c, v) \Rightarrow \exists r. l \in M(r) \wedge writes(r) \in \Phi)\ \wedge \\
\quad\quad (\epsilon = reduce_{id}(l, c, v) \Rightarrow \exists r. l \in M(r) \wedge reduces_{id}(r) \in \Phi)
\end{array}
\]

@@

An important insight from the proof of Theorem~\ref{thm:effects} is that 
it does not rely on the full definition of {\em valid\_interleave}.  Weakening 
{\em valid\_interleave} to {\em any\_interleave} (Figure~\ref{fig:validinterleave}), 
which  allows arbitrary interleavings of memory traces from subexpressions, 
is sufficient for the proof of soundness.  
The stronger constraints in {\em valid\_interleave}
(Figure~\ref{fig:validinterleave}) address the coherence of heap accesses;
{\em valid\_interleave} specifies permitted interleavings of memory operations for
the particular coherence modes on logical regions.

@@

To determine when parallel execution is safe, we start from the sequential execution trace and allow the reordering of 
adjacent heap operations that do not change the behavior of the application.  If we can show that it is safe to 
reorder any pair of operations that come from two different constituent traces, then any interleaving of the constituent
traces will be equivalent to a sequential execution and parallel execution is safe.  To
efficiently discover these cases at runtime, we require a test that can determine this property prior
to the actual execution of the tasks that create the traces.  We show that a test based on the subtask privileges and 
the current region mapping can soundly predict when this property will hold.
%If we can show that reordering is allowed
%between any two operations that come from different constituent traces, any interleaving of the constituent traces will
%be equivalent to the serialized execution and parallel execution was safe.  Finally, to allow the safety of parallel
%execution to be determined {\em before} the execution is actually performed, we show that a test based on the subtask
%privileges and the current region mapping can soundly predict when this property will hold.
We begin by defining a {\em non-interference} operator on two memory operations
$\epsilon_1 = op_1(l_1, c_1, v_1)$ and $\epsilon_2 = op_2(l_2, c_2, v_2)$:
$$
\begin{array}{l@{ }l}
\epsilon_1\ \nonint\ \epsilon_2 \Leftrightarrow & (op_1 = read \wedge op_2 = read)\ \vee \\
& (op_1 = reduce_{id_1} \wedge op_2 = reduce_{id_2} \wedge id_1 = id_2) \vee \\
& l_1 \not= l_2
\end{array}
$$
Reads have no side effects, and cannot change what another read returns.  The safety of the second case
follows from the requirement that reduction operations be commutative.  
Finally, accesses to different locations cannot affect each other.
We next show that this non-interference operator preserves the validity of an interleaving
of two or more traces when reordering a pair of memory operations.
\begin{lem}
\label{lem:nonintswap}
\rm
Let $S$ be a store, $C$ a clobber set, $\oton{E}, E'_a, E'_b$ memory traces, and
$\epsilon_1, \epsilon_2$ be two memory operations from $E_i$ and $E_j$ ($i \not= j$).  Then,
$$\begin{array}{l@{}l}
valid\_interleave&(S, C, E'_a \dplus [ \epsilon_1, \epsilon_2 ] \dplus E'_b, \oton{E}) \wedge \epsilon_1 \nonint \epsilon_2 \Rightarrow \\
 & valid\_interleave(S, C, E'_a \dplus [ \epsilon_2, \epsilon_1 ] \dplus E'_b, \oton{E}).
\end{array}$$
\end{lem}
%The proof follows from the definitions of {\em coherent} and {\em seq\_equiv} in Figure~\ref{fig:validinterleave}.

@@

We highlight an important aspect of a Legion
implementation that is different from other systems and relies on the
soundness of privileges.  Dynamic non-interference of 
memory operations can only be determined after 
evaluation of an expression is completed, and only at great expense, 
as illustrated by work on transactional
memory \cite{Harris05}.  
%However, many systems are willing to pay this cost to
%extract parallelism from operations that access aliased data. 
At the other extreme are systems like 
Jade \cite{Rinard98} and DPJ \cite{Bocchino11} that check non-interference 
statically, but must disallow aliasing to do so.  In contrast, Legion 
can verify non-interference of privileges
at runtime, which is much simpler and more efficient than checking
non-interference of dynamic memory traces.  Even though the privileges
themselves are static, the region mapping $M$ is dynamic.  Dynamically testing non-interference 
on the privileges of physical regions allows parallel execution in many more cases than a purely 
static analysis can achieve in the presence of aliasing.

@@

In cases where Legion cannot safely infer non-interference of
privileges (perhaps because two tasks actually access the same data in aliased regions),
relaxation of the constraints on execution order can
still be requested by the programmer through the use of coherence 
annotations on individual regions passed to a task.
%the default behavior of sequential execution can
%be avoided through the use of relaxed coherence.
The {\em atomic} coherence mode specifies that although two
tasks interfere due to accessing aliased regions, they may execute in either order, allowing
the task issued later in program order to possibly run before the task issued earlier 
in program order.  This relaxation only applies if all aliased regions are annotated with atomic coherence.
%or a more relaxed coherence mode (see Section~\ref{subsec:coherencesimult}).
To show this is safe, we define a relaxed version of non-interference for atomic coherence:
$$
\begin{array}{l@{}l}
op_1(l_1, c_1, v_1)\ \nonint^A\ op_2(l_2, c_2, v_2) \Leftrightarrow &op_1(l_1, c_1, v_1)\ \nonint\ op_2(l_2, c_2, v_2) \vee \\
& (c_1 = atomic \wedge c_2 = atomic)
\end{array}$$

@@

\texcomment{
Let $e_1$ and $e_2$ be well-typed Legion expressions using privileges $\Phi_1$ and
$\Phi_2$.  Now let $e_1'$ be some subexpression of $e_1$ and $e_2'$ be some 
subexpression of $e_2$, with corresponding privileges $\Phi_1'$ and $\Phi_2'$.
By Theorem~\ref{thm:parallelexec}, if the runtime can verify $\Phi_1 \nonint[M] \Phi_2$, then 
expressions $e_1$ and $e_2$ may be evaluated in parallel.  The evaluation of the subexpressions
$e_1'$ and $e_2'$ will therefore be allowed to run in parallel, and we must show that this is
permissible.  We do so by proving that any memory traces that can result from the evaluation
of the subexpression must be non-interfering (allowing parallel execution by
Lemma~\ref{lem:noninteffects}).
}
\begin{thm}
\label{thm:hiersched}
\rm
Let $e_1$ and $e_2$ be well-typed expressions using privileges $\Phi_1$ and
$\Phi_2$ respectively, where $\Phi_1 \nonint[M] \Phi_2$.  Let $e_1'$ be a subexpression of $e_1$ and $e_2'$ be a 
subexpression of $e_2$.  Any memory traces $E_1'$ of $e_1'$ and $E_2'$ of $e_2'$ resulting from evaluation of
$e_1$ and $e_2$ (with the usual consistent $M$, $L$, $H$, and $S$) are 
non-interfering.
\end{thm}
\texcomment{
\begin{proof}
Let $E_1$ be the result of an evaluation of $e_1$, with $E_1'$ being the memory trace from the
evaluation of $e_1'$ within the expression tree.  $E_1$ will be formed from a tree of valid
interleavings, each of which must include all the memory operations of each constituent trace.
By induction over the number of intermediate subexpressions between $e_1$ and $e_1'$, we
can show that any memory operation $\epsilon_1'$ that is in $E_1'$ must also be in $E_1$.
Similarly, any memory operation $\epsilon_2'$ that is in $E_2'$ must also be in $E_2$.  We have
$E_1 \nonint E_2$ from Lemma~\ref{lem:nonintpriv}, so and therefore $\epsilon_1' \nonint \epsilon_2'$.  Since
this holds for all $\epsilon_1'$ in $E_1'$ and all $\epsilon_2'$ in $E_2'$, we have $E_1' \nonint E_2'$.
\end{proof}
} The Legion task scheduler uses Theorem~\ref{thm:hiersched} as follows: 
sibling function calls (those invoked within the same
function body) $e_1$ and $e_2$ are checked for non-interference of their (dynamic)
privileges.  Since $e_1$ and $e_2$ are guaranteed to be created on the node on which their parent
is running, no communication is required to perform the non-interference
test.  If they interfere they are executed in program order or serialized
depending on their coherence specifications; otherwise they are
considered for execution as parallel subtasks.    If $e_1$ and $e_2$ are 
determined to be non-interfering and are scheduled in parallel on different 
remote processors then Theorem~\ref{thm:hiersched}
guarantees that there is no communication required between $e_1$ and $e_2$
to perform non-interference tests between their sub-tasks.  Therefore,
the runtime requires no communication for scheduling.
